\documentclass[10pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{setspace}

\setlength{\parskip}{\baselineskip}%
%\setlength{\parindent}{0pt}%
%\renewcommand{\baselinestretch}{1.4}

\let\oldquote\quote
\let\endoldquote\endquote
\renewenvironment{quote}[2][]
  {\if\relax\detokenize{#1}\relax
     \def\quoteauthor{#2}%
   \else
     \def\quoteauthor{#2~---~#1}%
   \fi
   \oldquote}
  {\par\nobreak\smallskip\hfill\textit{\quoteauthor}%
   \endoldquote\addvspace{\bigskipamount}}

\begin{document}
\begin{titlepage}\centering
{\scshape\huge An Epitome of the New Testament Epistles \par}
\vfill
{\scshape\large Daniel Hartig \par}
\vfill
\end{titlepage}
\singlespace
\section*{Introduction}

This work exists to be a summary of Christain thought as it has developed since Jesus ascended into heaven and left us on Earth. Jesus' teachings were heard by many, but not definitively written down at the time, in the way that Muhammed's teachings were codified within his lifetime. Therefore, Christian thought has always grappled with the proper interpretation of His words. Even the two most influential of Jesus' early followers disagreed on how to carry out a Christian life.
\begin{quote}{Galatians 2:11}
And when Kephas came to Antioch, I opposed him to his face because he clearly was wrong.
\end{quote}

Many years have passed since Christ walked on Earth with us, and much has the world changed. Some of the theological and moral challenges that lay before Man after two millenia could scarsely have been addressed by Christ on Earth. Fortunately, the Lord anticipated our plight, as he does all things, and sent and Advocate, the Holy Spirit, to aid us. From this Spirit, we may recieve Wisdom, if we ask for it.
\begin{quote}{James 1:5}
But if any of you lacks wisdom, he should ask God who gives to all generously and ungrudgingly, and he will be given it.
\end{quote}

You, who might read this book and who ask God for Wisdom, are not the first to seek answers. It would be foolish indeed to ignore those who have sought God's Truth over the past two millenia. Therefore, the goal of this work is to organize Christian thought to clearly show the connections from the foretellings of the Old Testaments, through Jesus' words recorded in the Gospel, to the Divinely Inspired writings of the Epistles of the New Testament. As we pass through each topic, this work will cover the writings in the Epistles in an exhaustive manner; that is, every verse from the letters of the New Testament--excepting only generic salutations and personal addresses--is covered in this work. Each verse is assigned to one or more topics, and each topic addresses the the fullness of the Divinely Inspired message. In addition, any relevant references from the Gospel and Old Testament are included to paint a complete picture of our Lord's guidance.

The quotations and discussion here are meant to be as viewpoint neutral as possible. The author wishes to avoid as much as possible choosing sides in the theoloical debates of today--or of the past. The goal is simply to present the Word in an organized fashion and in full context. With access to this guide, the reader may use his own God-granted Reason to apply this Word to his own life, praying all the while with faith and humility that God may grant him Wisdom.

It is the author's fervent hope that this work is but the first volume of many, which will carry the torch of Christian thought through time, from the Apostolic Age to the present. Thanks be to the many who have supported this work is it was written. May this work properly reflect the love and mercy of our Lord. 

\section*{Fundamental Assertions}

\section*{Acquiring Christian Knowledge}

\begin{quote}{Romans 1:1-6}
Paul, a slave of Christ Jesus, called to be an apostle and set apart for the gospel of God, which he promised previously through his prophets in the holy scriptures, the gospel about his Son, descended from David according to the flesh, but established as Son of God in power according to the spirit of holiness through resurrection from the dead, Jesus Christ our Lord. Through him we have recieved the grace of apostleship, to bring about the obedience of faith, for the sake of his name, among all the Gentiles, among whom are youalso, who are called to belong to Jesus Christ;
\end{quote}

\begin{quote}{Romans 1:9a}
God is my witness, whom I serve with my spirit in proclaiming the gospel of his Son...
\end{quote}

\begin{quote}{Romans 19-23}
For what can be known about God is evident to them, because God made it evident to them. Ever since the creation of the world, his invisible attriutes of eternal power and divinity have been able to be understood and perceived in what he has made.As a result, they have no excuse; for although they knew God they did not accord him glory as God or give him thank. Instead, they became vain in their reasoning, and their senseless minds were darkened. While claiming to be wise, they became fools sand exchanged the glory of the immortal God for the likeness of an image of mortal man or of birds or of four-legged animals or of snakes
\end{quote} 

\section*{The Nature of the Trinity}
\begin{quote}{Romans 1:1-4}
Paul, a slave of Christ Jesus, called to be an apostle and set apart for the gospel of God, which he promised previously through his prophets in the holy scriptures, the gospel about his Son, descended from David according to the flesh, but established as Son of God in power according to the spirit of holiness through resurrection from the dead, Jesus Christ our Lord.
\end{quote}

\section*{The Promise of Salvation}
\begin{quote}{Romans 1:16-18}
For I am not ashamed of the Gospel. It is the power of God for the salvation of everyone who believes; for the Jew first, and then the Greek. For in it is revealed the righteousness of God from faith to faith; as it is written, "The one who is righteous by faith will live". The wrath of God is indeed being revealed against every impiety and wickedness of those who supress the truth by their wickedness. 
\end{quote}

\subsection*{Justification through Faith}


\subsection*{The Valuable but Incomplete Law}


\subsection*{True Faith is Expressed}


\section*{Sin and Good Works}

\begin{quote}{Romans 1:24-25}
Therefore, God handed them over to impurity through the lusts of their hearts through the mutual degredation of their bodies. They exchanged the truth of God for a lie and revered and worshipped the creature rather than the creator, who is blessed forever. Amen.
\end{quote}
\begin{quote}{Romans 1:28}
And since they did not see fit to acknowledge God, God handed them over to their undiscerning mind to do what is improper.
\end{quote}
\begin{quote}{Romans 1:32}
Although they know the just decree of God that all who practice such things deserve death, they not only do them but give approval to those who practice them
\end{quote}

\subsection*{Sins of the Flesh Against Temperance}
\begin{quote}{Romans 1:26-27}
Therefore, God handed them over to degrading passions. Their females exchanged natural relations for unnatural and the males likelise ave up natural relations with females and burned with lust for one another. Males did shameful things with males and thus recieved in their own persons the due penalty for their perversity. 
\end{quote}

\subsection*{Pride and Greed Against Humility and Faith}
\begin{quote}{Romans 1:29-31}
They are filled with every form of wickedness, evil, greed, ad malice; full of envy, murder, rivalry, treachery, and spite. They are gossips and scandalmongers and they hate God. They are insolent, haughty, boastful, ingenious in their wickedness, and rebellious towards their parents. They are senseless, faithless, heartless, and ruthless. 
\end{quote}

\subsection*{Wrath Against Mercy}



\section*{Christian Discipline}

\subsection*{Communal and Individual Worship}

\subsection*{Holy Sacrament}

\subsection*{An Ordered Christian Community}


\end{document}